Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-05 GWLDCII.tex
extended remark 3.4 in a way that we need it later and removed the comments in the later spot about this

\begin{rmk}\label{rem:props of length 2 and 3} 
  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
 \begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\end{enumerate}
\end{rmk}

@@

Let \hlfix{$W_r := (\cP_{in}(q_r),[n])$}{technically has non supporting vertices. Want $(\cP_{in}(q_r),[i_r, k_r+1])$. However this is clear later. Do we care?}\note{No, we don't quite want that either because we don't want the newly shortened $q_r$ to be our propagator of length 2 -- maybe a slight change to the remark} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$. By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator. Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).

>>>>

\begin{rmk}\label{rem:props of length 2 and 3} 
  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
 \begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.  Furthermore, by the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in $[i,j]$ supports at least one propagator then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
\end{enumerate}
\end{rmk}

@@

Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$. By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator. Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).
